\bf The forestecology R package for fitting and assessing neighborhood models of the effect of interspecific competition on the growth of trees

### 2021-05-17 paper/paper.tex
tweak

\CommentTok{# Manually construct study region boundary}
\NormalTok{study_region_scbi <-}\StringTok{ }\KeywordTok{tibble}\NormalTok{(}
  \DataTypeTok{x =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{),}
  \DataTypeTok{y =} \KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{600}\NormalTok{, }\DecValTok{300}\NormalTok{)}
\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{sf_polygon}\NormalTok{()}

@@

We first manually define an \texttt{sf} object defining four folds that
partition the study region. We then use the output of the
\texttt{spatialBlock()} function from the \texttt{blockCV} package to
associate each tree in \texttt{growth\_scbi} to the correct
\texttt{foldID} \citep{valavi_blockcv_2019}.\footnote{In the Supporting
  Information we present an example where the folds themselves are
  created automatically, as opposed to manually as in the example.} This
\texttt{foldID} variable will be used in Section
\ref{spatial-cross-validation}.

@@

\NormalTok{blocks_scbi <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(}
  \KeywordTok{sf_polygon}\NormalTok{(fold1), }\KeywordTok{sf_polygon}\NormalTok{(fold2), }\KeywordTok{sf_polygon}\NormalTok{(fold3), }
  \KeywordTok{sf_polygon}\NormalTok{(fold4)}
\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{folds =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{n_fold) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{factor}\NormalTok{())}

\CommentTok{# Associate each observation to a fold}
\NormalTok{spatial_block_scbi <-}\StringTok{ }
\StringTok{  }\KeywordTok{spatialBlock}\NormalTok{(}\DataTypeTok{speciesData =}\NormalTok{ growth_scbi, }\DataTypeTok{k =}\NormalTok{ n_fold, }
               \DataTypeTok{selection =} \StringTok{"systematic"}\NormalTok{, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }
               \DataTypeTok{showBlocks =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{verbose =} \OtherTok{FALSE}\NormalTok{)}

\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{foldID =}\NormalTok{ spatial_block_scbi}\OperatorTok{$}\NormalTok{foldID }\OperatorTok{%>%}\StringTok{ }\KeywordTok{factor}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(focal_ID }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(focal_ID, dbh, comp) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{unnest}\NormalTok{(}\DataTypeTok{cols =} \StringTok{"comp"}\NormalTok{)}
\CommentTok{## # A tibble: 20 x 6}
\CommentTok{##   focal_ID   dbh comp_ID  dist comp_sp comp_basal_area}
\CommentTok{##      <dbl> <dbl>   <dbl> <dbl> <fct>             <dbl>}
\CommentTok{## 1        4  13.6    1836  7.48 tiam            0.0176 }
\CommentTok{## 2        4  13.6    1847  2.81 nysy            0.00332}
\CommentTok{## 3        4  13.6    1848  1.62 nysy            0.00396}
\CommentTok{## 4        4  13.6    1849  2.62 nysy            0.00535}
\CommentTok{## 5        4  13.6    1850  2.98 havi            0.00472}
\CommentTok{## # ... with 15 more rows}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(focal_ID, focal_sp, dbh, growth, growth_hat)}
\CommentTok{## # A tibble: 6,296 x 5}
\CommentTok{##   focal_ID focal_sp   dbh growth growth_hat}
\CommentTok{##      <dbl> <fct>    <dbl>  <dbl>      <dbl>}
\CommentTok{## 1        4 nysy     13.6   0.103     0.0809}
\CommentTok{## 2        5 havi      8.8   0.150     0.112 }
\CommentTok{## 3       79 tiam     47.7  -0.161     0.229 }
\CommentTok{## 4       80 caca      5.15  0.253     0.121 }
\CommentTok{## 5       96 libe      2.3   0.262     0.142 }
\CommentTok{## # ... with 6,291 more rows}
\end{Highlighting}
\end{Shaded}

@@

We also hope to extend the \texttt{forestecology} package's
functionality to account for a larger variety of models for tree growth.
One clear future direction would be to allow competition based on
species trait values rather than species identity. There is evidence
that traits predict competitive outcomes
\citep[\citet{lasky_trait-mediated_2014},
\citet{uriarte_trait_2010}]{kunstler_competitive_2012}. Thus an
extenstion of the model would allow \(lambda\) values to be a function
of the traits of competing species.

@@

>>>>

\CommentTok{# Manually construct study region boundary}
\NormalTok{study_region_scbi <-}\StringTok{ }\KeywordTok{tibble}\NormalTok{(}\DataTypeTok{x =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{), }\DataTypeTok{y =} \KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{, }
    \DecValTok{600}\NormalTok{, }\DecValTok{300}\NormalTok{)) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{sf_polygon}\NormalTok{()}

@@

We first manually define an \texttt{sf} object defining four folds that
partition the study region. We then use the output of the
\texttt{spatialBlock()} function from the \texttt{blockCV} package to
associate each tree in \texttt{growth\_scbi} to the correct
\texttt{foldID} \citep{valavi_blockcv_2019}. This \texttt{foldID}
variable will be used in Section \ref{spatial-cross-validation}.

@@

\NormalTok{blocks_scbi <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(}\KeywordTok{sf_polygon}\NormalTok{(fold1), }\KeywordTok{sf_polygon}\NormalTok{(fold2), }\KeywordTok{sf_polygon}\NormalTok{(fold3), }
    \KeywordTok{sf_polygon}\NormalTok{(fold4)) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{folds =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{n_fold) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{factor}\NormalTok{())}

\CommentTok{# Associate each observation to a fold}
\NormalTok{spatial_block_scbi <-}\StringTok{ }\KeywordTok{spatialBlock}\NormalTok{(}\DataTypeTok{speciesData =}\NormalTok{ growth_scbi, }\DataTypeTok{k =}\NormalTok{ n_fold, }
    \DataTypeTok{selection =} \StringTok{"systematic"}\NormalTok{, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{showBlocks =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{verbose =} \OtherTok{FALSE}\NormalTok{)}

\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{foldID =}\NormalTok{ spatial_block_scbi}\OperatorTok{$}\NormalTok{foldID }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{factor}\NormalTok{())}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(focal_ID }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(focal_ID, dbh, comp) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{unnest}\NormalTok{(}\DataTypeTok{cols =} \StringTok{"comp"}\NormalTok{)}
\CommentTok{## # A tibble: 20 x 6}
\CommentTok{##   focal_ID   dbh comp_ID  dist comp_sp comp_basal_area}
\CommentTok{##      <dbl> <dbl>   <dbl> <dbl> <fct>             <dbl>}
\CommentTok{## 1        4  13.6    1836  7.48 tiam            0.0176 }
\CommentTok{## 2        4  13.6    1847  2.81 nysy            0.00332}
\CommentTok{## 3        4  13.6    1848  1.62 nysy            0.00396}
\CommentTok{## 4        4  13.6    1849  2.62 nysy            0.00535}
\CommentTok{## 5        4  13.6    1850  2.98 havi            0.00472}
\CommentTok{## # ... with 15 more rows}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(focal_ID, focal_sp, dbh, growth, growth_hat)}
\CommentTok{## # A tibble: 6,296 x 5}
\CommentTok{##   focal_ID focal_sp   dbh growth growth_hat}
\CommentTok{##      <dbl> <fct>    <dbl>  <dbl>      <dbl>}
\CommentTok{## 1        4 nysy     13.6   0.103     0.0809}
\CommentTok{## 2        5 havi      8.8   0.150     0.112 }
\CommentTok{## 3       79 tiam     47.7  -0.161     0.229 }
\CommentTok{## 4       80 caca      5.15  0.253     0.121 }
\CommentTok{## 5       96 libe      2.3   0.262     0.142 }
\CommentTok{## # ... with 6,291 more rows}
\end{Highlighting}
\end{Shaded}

@@

We also hope to extend the \texttt{forestecology} package's
functionality to account for a larger variety of models for tree growth.
One clear future direction would be to allow competition based on
species trait values rather than species identity. There is evidence
that traits predict competitive outcomes
\citep[\citet{lasky_trait-mediated_2014},
\citet{uriarte_trait_2010}]{kunstler_competitive_2012}. Thus an
extension of the model would allow \(\lambda\) values from Equation
\ref{eq:model} to be a function of the traits of competing species.

@@

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

This code replicates Figure \ref{fig:scbi-simulation}: A comparison of
root mean squared error of models for standard, permuted, and spatial
cross- validated error estimates.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{library}\NormalTok{(tidyverse)}
\KeywordTok{library}\NormalTok{(lubridate)}
\KeywordTok{library}\NormalTok{(here)}
\KeywordTok{library}\NormalTok{(sf)}
\KeywordTok{library}\NormalTok{(viridis)}
\KeywordTok{library}\NormalTok{(forestecology)}
\KeywordTok{library}\NormalTok{(blockCV)}
\KeywordTok{library}\NormalTok{(tictoc)}

\CommentTok{# Compute growth of trees based on census data -------------------------}
\NormalTok{census_}\DecValTok{2013}\NormalTok{_scbi <-}\StringTok{ }\KeywordTok{here}\NormalTok{(}\StringTok{"paper/scbi.stem2.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{read_csv}\NormalTok{() }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(stemID, sp, }\DataTypeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{date =} \KeywordTok{mdy}\NormalTok{(date), }\DataTypeTok{dbh =} \KeywordTok{as.numeric}\NormalTok{(dbh)}\OperatorTok{/}\DecValTok{10}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(gx }\OperatorTok{<}\StringTok{ }\DecValTok{300}\NormalTok{, }\KeywordTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{census_}\DecValTok{2018}\NormalTok{_scbi <-}\StringTok{ }\KeywordTok{here}\NormalTok{(}\StringTok{"paper/scbi.stem3.csv"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{read_csv}\NormalTok{() }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(stemID, sp, }\DataTypeTok{date =}\NormalTok{ ExactDate, gx, gy, dbh, codes, status) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{date =} \KeywordTok{mdy}\NormalTok{(date), }\DataTypeTok{dbh =} \KeywordTok{as.numeric}\NormalTok{(dbh)}\OperatorTok{/}\DecValTok{10}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(gx }\OperatorTok{<}\StringTok{ }\DecValTok{300}\NormalTok{, }\KeywordTok{between}\NormalTok{(gy, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{))}

\NormalTok{growth_scbi <-}\StringTok{ }\KeywordTok{compute_growth}\NormalTok{(}\DataTypeTok{census_1 =}\NormalTok{ census_}\DecValTok{2013}\NormalTok{_scbi, }\DataTypeTok{census_2 =}\NormalTok{ census_}\DecValTok{2018}\NormalTok{_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(}\OperatorTok{!}\KeywordTok{str_detect}\NormalTok{(codes, }\StringTok{"R"}\NormalTok{)), }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{)}

\CommentTok{# Add spatial information ----------------------------------------------}
\CommentTok{# Define buffer region using competitive distance range}
\NormalTok{comp_dist <-}\StringTok{ }\FloatTok{7.5}

\NormalTok{study_region_scbi <-}\StringTok{ }\KeywordTok{tibble}\NormalTok{(}\DataTypeTok{x =} \KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{0}\NormalTok{, }\DecValTok{0}\NormalTok{), }\DataTypeTok{y =} \KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{, }
    \DecValTok{600}\NormalTok{, }\DecValTok{300}\NormalTok{)) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{sf_polygon}\NormalTok{()}

\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{add_buffer_variable}\NormalTok{(}\DataTypeTok{size =}\NormalTok{ comp_dist, }\DataTypeTok{region =}\NormalTok{ study_region_scbi)}

\CommentTok{# Manually define spatial blocks to act as folds}
\NormalTok{fold1 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{450}\NormalTok{))}
\NormalTok{fold2 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{300}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{450}\NormalTok{))}
\NormalTok{fold3 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{600}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{0}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\NormalTok{fold4 <-}\StringTok{ }\KeywordTok{rbind}\NormalTok{(}\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{450}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{300}\NormalTok{, }\DecValTok{600}\NormalTok{), }\KeywordTok{c}\NormalTok{(}\DecValTok{150}\NormalTok{, }\DecValTok{600}\NormalTok{))}
\NormalTok{n_fold <-}\StringTok{ }\DecValTok{4}

\NormalTok{blocks_scbi <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(}\KeywordTok{sf_polygon}\NormalTok{(fold1), }\KeywordTok{sf_polygon}\NormalTok{(fold2), }\KeywordTok{sf_polygon}\NormalTok{(fold3), }
    \KeywordTok{sf_polygon}\NormalTok{(fold4)) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{folds =} \KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\NormalTok{n_fold) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{factor}\NormalTok{())}

\CommentTok{# Associate each observation to a fold}
\NormalTok{SpatialBlock_scbi <-}\StringTok{ }\KeywordTok{spatialBlock}\NormalTok{(}\DataTypeTok{speciesData =}\NormalTok{ growth_scbi, }\DataTypeTok{k =}\NormalTok{ n_fold, }
    \DataTypeTok{selection =} \StringTok{"systematic"}\NormalTok{, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{showBlocks =} \OtherTok{FALSE}\NormalTok{, }\DataTypeTok{verbose =} \OtherTok{FALSE}\NormalTok{)}

\NormalTok{growth_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{foldID =}\NormalTok{ SpatialBlock_scbi}\OperatorTok{$}\NormalTok{foldID }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{factor}\NormalTok{())}

\CommentTok{# Compute focal versus competitor tree information ---------------------}
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{create_focal_vs_comp}\NormalTok{(comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{)}

\CommentTok{# Fit model and make predictions ---------------------------------------}
\CommentTok{# Number of permutation shuffles:}
\NormalTok{num_shuffle <-}\StringTok{ }\DecValTok{49}

\CommentTok{# Save results here}
\NormalTok{run_time <-}\StringTok{ }\DecValTok{0}
\NormalTok{observed_RMSE <-}\StringTok{ }\DecValTok{0}
\NormalTok{observed_RMSE_CV <-}\StringTok{ }\DecValTok{0}
\NormalTok{shuffle_RMSE <-}\StringTok{ }\KeywordTok{vector}\NormalTok{(}\StringTok{"list"}\NormalTok{, }\DecValTok{1}\NormalTok{)}
\NormalTok{shuffle_RMSE_CV <-}\StringTok{ }\KeywordTok{vector}\NormalTok{(}\StringTok{"list"}\NormalTok{, }\DecValTok{1}\NormalTok{)}
\NormalTok{filename <-}\StringTok{ }\KeywordTok{here}\NormalTok{(}\StringTok{"paper/simulation_results/"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{str_c}\NormalTok{(}\StringTok{"2021-03-03_scbi_"}\NormalTok{, num_shuffle, }\StringTok{"_shuffles"}\NormalTok{)}

\CommentTok{# Run all simulations 0. Setup simulation for this species type ----}
\CommentTok{# Start clock}
\KeywordTok{tic}\NormalTok{()}

\CommentTok{# 1. Compute observed test statistic: RMSE with no cross-validation ----}
\CommentTok{# Fit model (compute posterior parameters)}
\NormalTok{comp_bayes_lm_scbi <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{comp_bayes_lm}\NormalTok{(}\DataTypeTok{prior_param =} \OtherTok{NULL}\NormalTok{, }\DataTypeTok{run_shuffle =} \OtherTok{FALSE}\NormalTok{)}

\CommentTok{# Make predictions and compute RMSE}
\NormalTok{observed_RMSE <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{growth_hat =} \KeywordTok{predict}\NormalTok{(comp_bayes_lm_scbi, focal_vs_comp_scbi)) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{pull}\NormalTok{(.estimate)}

\CommentTok{# 2. Compute observed test statistic: RMSE with cross-validation -------}
\NormalTok{observed_RMSE_CV <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{pull}\NormalTok{(.estimate)}

\CommentTok{# 3. Permutation distribution: RMSE with no cross-validation -----------}
\CommentTok{# Compute num_shuffle permutation test statistics}
\NormalTok{shuffle_RMSE <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\DataTypeTok{length =}\NormalTok{ num_shuffle)}
\ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\NormalTok{num_shuffle) \{}
    \CommentTok{# Fit model (compute posterior parameters) with shuffling}
\NormalTok{    comp_bayes_lm_scbi <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{comp_bayes_lm}\NormalTok{(}\DataTypeTok{prior_param =} \OtherTok{NULL}\NormalTok{, }\DataTypeTok{run_shuffle =} \OtherTok{TRUE}\NormalTok{)}

    \CommentTok{# Make predictions and compute RMSE}
\NormalTok{    shuffle_RMSE[j] <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{growth_hat =} \KeywordTok{predict}\NormalTok{(comp_bayes_lm_scbi, focal_vs_comp_scbi)) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{pull}\NormalTok{(.estimate)}
\NormalTok{\}}

\CommentTok{# 4. Permutation distribution: RMSE with cross-validation --------------}
\CommentTok{# Compute num_shuffle permutation test statistics}
\NormalTok{shuffle_RMSE_CV <-}\StringTok{ }\KeywordTok{numeric}\NormalTok{(}\DataTypeTok{length =}\NormalTok{ num_shuffle)}

\CommentTok{# Compute num_shuffle permutation test statistics}
\ControlFlowTok{for}\NormalTok{ (j }\ControlFlowTok{in} \DecValTok{1}\OperatorTok{:}\NormalTok{num_shuffle) \{}
    \CommentTok{# Compute and save RMSE}
\NormalTok{    shuffle_RMSE_CV[j] <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{run_shuffle =} \OtherTok{TRUE}\NormalTok{) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{rmse}\NormalTok{(}\DataTypeTok{truth =}\NormalTok{ growth, }\DataTypeTok{estimate =}\NormalTok{ growth_hat) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{pull}\NormalTok{(.estimate)}

    \CommentTok{# Status update}
    \KeywordTok{str_c}\NormalTok{(}\StringTok{"Shuffle with permutation "}\NormalTok{, j, }\StringTok{" at "}\NormalTok{, }\KeywordTok{Sys.time}\NormalTok{()) }\OperatorTok{%>%}
\StringTok{        }\KeywordTok{print}\NormalTok{()}
\NormalTok{\}}

\CommentTok{# 5. Save results ----}
\NormalTok{clock <-}\StringTok{ }\KeywordTok{toc}\NormalTok{(}\DataTypeTok{quiet =} \OtherTok{TRUE}\NormalTok{)}
\NormalTok{run_time <-}\StringTok{ }\NormalTok{clock}\OperatorTok{$}\NormalTok{toc }\OperatorTok{-}\StringTok{ }\NormalTok{clock}\OperatorTok{$}\NormalTok{tic}

\NormalTok{model_comp_tbl <-}\StringTok{ }\KeywordTok{tibble}\NormalTok{(}\DataTypeTok{run_time =}\NormalTok{ run_time, }\DataTypeTok{observed_RMSE =}\NormalTok{ observed_RMSE, }
    \DataTypeTok{observed_RMSE_CV =}\NormalTok{ observed_RMSE_CV, }\DataTypeTok{shuffle_RMSE =}\NormalTok{ shuffle_RMSE, }\DataTypeTok{shuffle_RMSE_CV =}\NormalTok{ shuffle_RMSE_CV, }
\NormalTok{    )}
\KeywordTok{save}\NormalTok{(model_comp_tbl, }\DataTypeTok{file =}\NormalTok{ filename }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{str_c}\NormalTok{(}\StringTok{".RData"}\NormalTok{))}

\CommentTok{# Visualize results ----------------------------------------------------}
\NormalTok{model_comp <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(model_comp_tbl }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(run_time, }\DataTypeTok{observed =}\NormalTok{ observed_RMSE, }\DataTypeTok{shuffle =}\NormalTok{ shuffle_RMSE) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CV =} \OtherTok{FALSE}\NormalTok{), model_comp_tbl }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{select}\NormalTok{(run_time, }\DataTypeTok{observed =}\NormalTok{ observed_RMSE_CV, }\DataTypeTok{shuffle =}\NormalTok{ shuffle_RMSE_CV) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{CV =} \OtherTok{TRUE}\NormalTok{)) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{gather}\NormalTok{(type, RMSE, }\OperatorTok{-}\KeywordTok{c}\NormalTok{(run_time, CV))}

\NormalTok{model_comp_observed <-}\StringTok{ }\NormalTok{model_comp }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(type }\OperatorTok{==}\StringTok{ "observed"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{unnest}\NormalTok{(}\DataTypeTok{cols =} \KeywordTok{c}\NormalTok{(RMSE))}
\NormalTok{model_comp_shuffle <-}\StringTok{ }\NormalTok{model_comp }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{filter}\NormalTok{(type }\OperatorTok{==}\StringTok{ "shuffle"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{unnest}\NormalTok{(}\DataTypeTok{cols =} \KeywordTok{c}\NormalTok{(RMSE))}

\NormalTok{cv_plot <-}\StringTok{ }\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_vline}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ model_comp_observed, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{xintercept =}\NormalTok{ RMSE, }
    \DataTypeTok{col =}\NormalTok{ CV), }\DataTypeTok{linetype =} \StringTok{"dashed"}\NormalTok{, }\DataTypeTok{show.legend =}\NormalTok{ F) }\OperatorTok{+}\StringTok{ }\KeywordTok{geom_histogram}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ model_comp_shuffle, }
    \KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ RMSE, }\DataTypeTok{fill =}\NormalTok{ CV), }\DataTypeTok{bins =} \DecValTok{50}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{labs}\NormalTok{(}\DataTypeTok{fill =} \StringTok{"Cross-validated?"}\NormalTok{, }
    \DataTypeTok{x =} \KeywordTok{expression}\NormalTok{(}\KeywordTok{paste}\NormalTok{(}\StringTok{"RMSE (cm "}\NormalTok{, y}\OperatorTok{^}\NormalTok{\{}
        \DecValTok{-1}
\NormalTok{    \}, }\StringTok{")"}\NormalTok{))) }\OperatorTok{+}\StringTok{ }\KeywordTok{scale_color_viridis}\NormalTok{(}\DataTypeTok{discrete =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{option =} \StringTok{"D"}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{scale_fill_viridis}\NormalTok{(}\DataTypeTok{discrete =} \OtherTok{TRUE}\NormalTok{) }\OperatorTok{+}\StringTok{ }
\StringTok{    }\KeywordTok{theme_light}\NormalTok{()}
\NormalTok{cv_plot}

\NormalTok{filename }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{str_c}\NormalTok{(}\StringTok{".pdf"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{    }\KeywordTok{ggsave}\NormalTok{(}\DataTypeTok{plot =}\NormalTok{ cv_plot, }\DataTypeTok{width =} \DecValTok{16}\OperatorTok{/}\DecValTok{2}\NormalTok{, }\DataTypeTok{height =} \DecValTok{9}\OperatorTok{/}\DecValTok{2}\NormalTok{)}
\end{Highlighting}
\end{Shaded}
